Postural developments modulate children's visual access to social information

### 2018-10-12 writeup-cogsci/cogsci2018_remakePlots.Rmd
r file that remakes plots for poster

ggarrange(p1,p2)
fig1=ggarrange(p1,p2)
ggsave("Fig3-TimebyPos.png", width = 5, height = 5,unit =  "in", plot = fig1, path="./figs/", device = "png",dpi = 300)
```
## Changes in Posture and Orientation
The proportion of time infants spent sitting decreased with age, and the proportion of time infants spent standing increased with age. Both 8-month-olds and 12-month-olds spent equivalent amounts of time lying/crawling, which was markedly decreased in the 16-month-olds, who spent most of their time sitting or standing (see Figure \ref{fig:posture}).  We also observed changes in children's orientation relative to their caregivers: the 8-month-olds spent more time with their caregiver behind them supporting their sitting positions (see Figure \ref{fig:posture}).

@@

fig4=ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
  geom_jitter(width = .25) +
  geom_smooth(size=1) +
  scale_x_continuous(breaks=c(8,12,16)) +
  scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
  labs(y = "Prop. detected", x = element_blank()) +
  theme_few() + 
  theme(legend.position="none") +
  facet_grid(~detectorType)

ggsave("Fig4-DetbyAge.png", width = 5, height = 4,unit =  "in", plot = fig4, path="./figs/", device = "png",dpi = 300)
```

>>>>

ggarrange(p1,p2, nrow=1)
fig1=ggarrange(p1,p2, ncol=1)
ggsave("Fig3-TimebyPos.png", width = 4, height = 4,unit =  "in", plot = fig1, path="./figs/", device = "png",dpi = 300)
```
## Changes in Posture and Orientation
The proportion of time infants spent sitting decreased with age, and the proportion of time infants spent standing increased with age. Both 8-month-olds and 12-month-olds spent equivalent amounts of time lying/crawling, which was markedly decreased in the 16-month-olds, who spent most of their time sitting or standing (see Figure \ref{fig:posture}).  We also observed changes in children's orientation relative to their caregivers: the 8-month-olds spent more time with their caregiver behind them supporting their sitting positions (see Figure \ref{fig:posture}).

@@

fig4=ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
  geom_jitter(width = .25) +
  geom_smooth(size=1) +
  scale_x_continuous(breaks=c(8,12,16)) +
  scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
  scale_colour_grey(start=.2, end=.6) +
  labs(y = "Prop. detected", x = element_blank()) +
  theme_few() + 
  theme(legend.position="none") +
  facet_wrap(~detectorType, ncol=1)

ggsave("Fig4-DetbyAge.png", width = 3, height = 4,unit =  "in", plot = fig4, path="./figs/", device = "png",dpi = 300)
```
